Figures and Analysis for 2023 Manuscript

### 2023-12-05 data-raw/Manuscript2023_Workflow.Rmd
Expanded documentation for Manuscript Vignette

1. Pulling Data from CvTdb  
  - Minimal `pk` object  
2. Running all possible fitting options  
  - Evaluating fitting options  
  - Head-to-head comparison of pooled vs joint models  
3. Running dose-normalized joint fits  
4. Analysis Plots  
  - CvTdb replicate variation (Figure 4A)  
  - CvTdb replicate variation over ADME-normalized time (Figure 4B)  
  - CvTdb concentration and final time-point distributions (Supplementary Figure 1)  
  - invivoPKfit fit option selection (Supplementary Table 1)  
  - invivoPKfit model performance (Supplementary Figure 2)  
  - Model performance vs Data variability (Figure 5)  
  - Goodness of fit plots (Figure 6)  
  - Fits that may be improved (Supplementary Figure 3)  
5. Lombardo Analysis  
  - Chemicals included  
  - Comparison of derived TK stats  (Figure 7A)  
  - Histograms for Steady-state Volume of Dist. and Total Clearance (Supplemental Figure 4)
6. Benchmarking invivoPKfit
  - Parallelization speeds up the process of fitting (Supplementary Figure 5)

@@

```{r pk_obj_fromSQL}

@@

### Figure 4A: Replicated timepoint variation in CvTdb
```{r fig4A, eval=FALSE}

@@

### Figure 2
```{r Explain-Heirarchical-Model, eval=FALSE}
# Note that the data will run one "Series" of time point at a time
my_1comp <- function(t, F_V, kelim, kabs, sd = 0) {
  sd + (F_V * (kabs * (exp(-kelim * t) - exp(-kabs * t))) / (kabs - kelim))
}

>>>>

1. Pulling Data from CvTdb  
  - Minimal `pk` object  
2. Running all possible fitting options  
  - Evaluating fitting options  
  - Head-to-head comparison of pooled vs joint models  
3. Running dose-normalized joint fits  
4. Analysis Plots  
  - CvTdb replicate variation (Figure 4A & Alternative)  
  - CvTdb replicate variation over ADME-normalized time (Figure 4B)  
  - CvTdb concentration and final time-point distributions (Supplementary Figure 1)  
  - invivoPKfit fit option selection (Supplementary Table 1)  
  - invivoPKfit model performance (Supplementary Figure 2)  
  - Model performance vs Data variability (Figure 5 and Alternative)  
  - Goodness of fit plots (Figure 6)  
  - Fits that may be improved (Supplementary Figure 3)  
5. Lombardo Analysis  
  - Chemicals included  
  - Comparison of derived TK stats  (Figure 7A)  
  - Histograms for Steady-state Volume of Dist. and Total Clearance (Supplemental Figure 4)
6. Benchmarking invivoPKfit
  - Parallelization speeds up the process of fitting (Supplementary Figure 5)

@@

The following chunk shows the column/field mapping from the `cvt` object and
the `pk` object needed for invivoPKfit analysis.

```{r pk_obj_fromSQL, eval=FALSE}

@@

### Figure 4A: Replicated timepoint variation in CvTdb

```{r fig4A, eval=FALSE}

@@

### Figure 2: Example Fits to Explain Joint vs Pooled Models

```{r Explain-Heirarchical-Model, eval=FALSE}
# Note that the data will run one "Series" of time point at a time
my_1comp <- function(t, F_V, kelim, kabs, sd = 0) {
  sd + (F_V * (kabs * (exp(-kelim * t) - exp(-kabs * t))) / (kabs - kelim))
}
